A Large and Variable Leading Tail of Helium in a Hot Saturn Undergoing Runaway Inflation

### 2023-09-07 paper/paper1/ms.tex
Referee report item 4
item 3 from the referee report (working backwards)

Finally, we detect a much weaker but still significant post-egress blue-shifted absorption.  This lobe appears to decrease linearly in wavelength, corresponding to a characteristic blueshift increasing from near zero at transit midpoint to 80~km/s at 12 hours after transit.  It exhibits a slightly lower line-of-sight velocity distribution of 50 km/s, about half of the peak during transit.

@@

Figure \ref{fig:KeplerianShear} shows an illustration of Keplerian shear adapted to the system properties of \hatpb.  In this shear-dominated scenario, the planetary wind launches primarily from the dayside, with relatively little or no wind launched from the nightside.  The planet wind initially launches radially outward from the exobase, with the strongest wind located near the sub-stellar point, the line connecting the planet to the star along the vertical axis in the figure.  Inefficient grazing incidence heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemispherical shape, but more concentration along the star-planet line.  The gas increasingly experiences the star's Keplerian potential past the Roche lobe, accelerating in the direction of orbital motion, $+x$.  The accelerating column eventually overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.  The mass loss has to be large enough to shield the material to make it observable in the metastable \ion{He}{1} 10833 \AA~triplet.

@@

>>>>

Finally, we detect a much weaker but still significant post-egress blue-shifted absorption \edit1{perceptible in Figure \ref{fig:HPFscanResid} at 0.1 in phase and about 10831 \AA}.  This lobe appears to decrease linearly in wavelength, corresponding to a characteristic blueshift increasing from near zero at transit midpoint to 80~km/s at 12 hours after transit.  It exhibits a slightly lower line-of-sight velocity distribution of 50 km/s, about half of the peak during transit.

@@

Figure \ref{fig:KeplerianShear} shows an illustration of Keplerian shear adapted to the system properties of \hatpb.  In this shear-dominated scenario, the planetary wind launches primarily from the dayside, with relatively little or no wind launched from the nightside.  The planet wind initially launches radially outward from the exobase, with the strongest wind located near the sub-stellar point, the line connecting the planet to the star along the vertical axis in the figure.  Inefficient grazing incidence heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemispherical shape, but more concentration along the star-planet line.  \edit1{The gas increasingly experiences Keplerian shear past the Roche lobe, manifesting as prograde acceleration.  In the rotating frame, the Coriolis effect causes the inward-moving gas to advance ahead of the planet. In the inertial frame, the gas is launched onto an orbit with a smaller periapse than the planet, and so runs ahead.  The accelerating flow} eventually overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.  The mass loss has to be large enough to shield the material to make it observable in the metastable \ion{He}{1} 10833 \AA~triplet.

@@

\edit1{\subsection{Prospect for orbital evolution}
  Content here...}
